\documentclass{article}
\usepackage{amssymb,amsmath,amsfonts,mathtools} % useful math fonts and symbols
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}
\usepackage{geometry}
\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}

\title{Activity 5 - Market for Lemons}
\author{EC327 Game Theory}
\date{February 22, 2024}

\begin{document}
    
\maketitle

\section*{Game Description}
In Top Gear Season 21 Episode 1, the three presenters, Jeremy, James, and Richard
are challenged by the producers to each buy a 'hot' hatchback 
for less than \pounds 800.

\url{https://youtu.be/7RDziX3sqHI?list=PLWpVvJ8o7wzy1a760RwP9tAIR2EPx0FRu}

For the purposes of this game, 
suppose that there are two levels of quality in the Craigslist used car market.
\begin{itemize}
  \item \textbf{"Good"} quality cars are worth \pounds 600 in resale value.
  \item \textbf{"Lemons"} are only worth \pounds 200 in scrap value.
\end{itemize}

\section*{Activity Rules}

\begin{itemize}
    \item Break into groups of 4. 
    Pick three people to be presenters (buyers of cars)
    and one person to be the Craigslist dealer.
    
    \item I will give each dealer 3 different cars to sell.
    They can observe the quality of the car. 
    \textbf{But don't show the quality to the buyers!!}

    \item Dealers earn profit based on the price they sell each car for 
    minus its actual value.

    \item Presenters have an \pounds 800 budget to buy a car.
    The winner of the challenge will be the presenter who 
    has the highest resale value of their car 
    which is the true value of the car $+$ whatever budget they had left over to improve it.

\end{itemize}

\begin{enumerate}
  \item The Craigslist dealer will auction off one car at a time.
  They can choose the order of the cars they auction and starting prices.

  \item The presenters will bid on the dealer's cars until either everyone has bought a car 
  or presenters have not found any cars they would be willing to buy 
  at prices the dealer is offering
  (but this means they lose the challenge).
  Presenters can only buy one car.

  \item Buyers will reveal the quality of the car they received
  and calculate who had the highest resale value.

  \item Record the prices and true quality of all cars at your table.

  \item Collect your car cards and hand them to the next table.
  Repeat steps 1-4 with your new car cards.
\end{enumerate}

\end{document}
