\documentclass[addpoints ]{exam}

\usepackage{amssymb, amsmath, amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{multirow,array} % for payoff matrix formatting
\usepackage{hyperref}
\usepackage{xcolor}
\hypersetup{
  colorlinks = true,
  linkcolor  = gray,
  urlcolor   = blue
}

\definecolor{crimson}{RGB}{ 170, 4, 36 }
\definecolor{darkblue}{RGB}{ 4, 47, 170 }
\definecolor{brown}{RGB}{ 111, 71, 2 }
\definecolor{periwinkle}{RGB}{ 90, 177, 204 }
\definecolor{ducksgreen}{HTML}{007030}

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}
\pagestyle{headandfoot}
\lhead{EC327 Game Theory}
\chead{Homework 3}
\rhead{Fall 2024}
\runningheadrule

\title{
    \textbf{Econ 327: Game Theory} \\ 
    Homework $\#3$
    }
\author{University of Oregon}
\date{Due: Nov. 15$^{th}$}

% exam-type question formatting
\renewcommand{\thequestion}{\textbf{Question \arabic{question}}}
\bracketedpoints

\begin{document}

\maketitle

\begin{center}
  \gradetable[h][questions]
\end{center}

\vspace{0.5in}

\begin{center}
  \textbf{For homework assignments:}
\end{center}

\begin{itemize}

%  \item DO NOT write your name:
%  this assignment will be graded anonymously. 
%  If you want to, you can include your student ID instead.

  \item Complete \textit{all} questions and parts.
  % I will select one question at random to be graded
  % according to the rubric on Canvas.

  \item You may choose to work with others,
  but everyone must submit to Canvas individually.
  Please include the names of everyone who you worked with 
  below your own name.
 
\end{itemize}

\vspace{1.0in}

\makebox[.6\textwidth]{Name\enspace\hrulefill}

\vspace{0.5in}

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
  \textbf{Note:}
  All parts of Questions 1 and 2 are either directly from 
  or adapted from problems in  
  Dixit, Skeath and Reiley, \textit{Games of Strategy}, Fourth Edition. 
  }}}
\end{center}

\newpage

\begin{questions}

%------------------------------------------------------------------%

\question[20]
\textbf{Multiple Choice}

\begin{parts}

  \part Consider the game of Rock, Paper, Scissors:
  \begin{table}[h!]
    \begin{center}
    \begin{tabular}{*{5}{c|}}
      \multicolumn{2}{c}{} & \multicolumn{3}{c}{Lisa} \\\cline{3-5}
      \multicolumn{1}{c}{} &          & Rock    & Scissors & Paper   \\\cline{2-5}
      \multirow{3}*{Bart}  & Rock     &   0,  0 &  10, -10 & -10, 10 \\\cline{2-5}
                           & Scissors & -10, 10 &   0,   0 &  10,-10 \\\cline{2-5}
                           & Paper    &  10,-10 & -10,  10 &   0   0 \\\cline{2-5} 
    \end{tabular}
    \end{center}
  \end{table}

  Suppose that Lisa announced she would use a mixture in which 
  she chooses Rock with 40\% probability, Scissors with 30\% probability,
  and Paper with 30\% probability.
  What is Bart's best response to this strategy choice?
  \begin{choices}
    \choice Rock
    \CorrectChoice Paper
    \choice Scissors
    \choice Mixed strategy of Rock with 1/3, Scissors with 1/3,
    and Paper with 1/3.
  \end{choices}

  \part Consider the following game:
  \begin{table}[!h]
  \begin{center}
    \begin{tabular}{*{4}{c|}}
      \multicolumn{2}{c}{} &
      \multicolumn{2}{c}{Colin} \\ \cline{3-4}
      \multicolumn{1}{c}{} &       & $DL$   & $CC$   \\ \cline{2-4}
      \multirow{2}*{Rowena} & $DL$ & 4, 4 & 4, 1 \\ \cline{2-4}
                            & $CC$ & 1, 1 & 6, 6 \\ \cline{2-4} 
    \end{tabular}
  \end{center}
  \end{table}

  How many Nash Equilibria are there \textit{including mixed strategies}?
  \begin{choices}
    \choice one equilibrium
    \choice two equilbria
    \CorrectChoice three equilibria
    \choice an infinite number of equilibria
  \end{choices}

  \part 
  Consider the strategic form game below:

  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{*{4}{c|}}
        \multicolumn{2}{c}{} & \multicolumn{2}{c}{Column} \\ \cline{3-4}
        \multicolumn{1}{c}{} &    & Left & Right \\ \cline{2-4}
        \multirow{2}*{Row} & Up   & 4,1 & 2,2 \\ \cline{2-4}
                           & Down & 1,1 & 3,0 \\ \cline{2-4}
      \end{tabular}
    \end{center}
  \end{table}

  How many Nash Equilibria are there \textit{including mixed strategies}?

  \begin{choices}
    \CorrectChoice one equilibrium
    \choice two equilbria
    \choice three equilibria
    \choice an infinite number of equilibria
  \end{choices}

  \newpage

  \part
  Find the mixed-strategy Nash equilibrium for the simultaneous game below:

  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{*{4}{c|}}
        \multicolumn{2}{c}{}  & \multicolumn{2}{c}{Pitcher} \\ \cline{3-4}
        \multicolumn{1}{c}{}  &                              & Throw fastball & Throw curve \\ \cline{2-4}
        \multirow{2}*{Batter} & Anticipate fastball          & 0.30, 0.70     & 0.20, 0.80   \\ \cline{2-4}
                              & Anticipate curve             & 0.15, 0.85     & 0.35, 0.65\\ \cline{2-4}
      \end{tabular}
    \end{center}
  \end{table}

  where $a$ represents the probability of Batter playing Anticipate fastball
  and $t$ represents the probability of Pitcher playing Throw fastball.

  \begin{choices}
    \choice ($t = 1/3$, $a = 2/3$)
    \choice ($t = 1/4$, $a = 1/4$)
    \CorrectChoice ($t = 1/2$, $a = 2/3$)
    \choice ($t = 1/6$, $a = 3/4$)
  \end{choices}

  \part 
  For this simplified version of the Cold War:

  \begin{table}[h!]
    \begin{center}
      \begin{tabular}{*{4}{c|}}
        \multicolumn{2}{c}{} & \multicolumn{2}{c}{Soviet Union} \\ \cline{3-4}
        \multicolumn{1}{c}{} &                   & Restrained & Aggressive \\ \cline{2-4}
        \multirow{2}*{United States} & Restrained & 4,3        & 1,4        \\ \cline{2-4}
                                    & Aggressive & 3,1        & 2,2        \\ \cline{2-4}
      \end{tabular}
    \end{center}
  \end{table}

  If one player could make a \textit{strategic move} in a first stage of this game,
  which of the following would be a strategic move which would be \textit{credible}
  and would improve the payoff of the player who made the strategic move?

  \begin{choices}
    \choice The Soviet Union commits to only playing Aggressive
    \choice The Soviet Union promises to play Restrained if the US does too
    \choice The United States develops a reputation of always playing restrained 
    \CorrectChoice The United States threatens to play Aggressive unless the Soviet Union plays Restrained
  \end{choices}
  
\end{parts}

%------------------------------------------------------------------%

\newpage

\question
Consider the following game:
\footnote{Dixit, Skeath, and McAdams, pg 250}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{*{4}{c|}}
      \multicolumn{2}{c}{} & \multicolumn{2}{c}{Colin} \\ \cline{3-4}
      \multicolumn{1}{c}{} &      & Yes   & No  \\ \cline{2-4}
      \multirow{2}*{Rowena} & Yes & $x,x$ & $0,1$ \\ \cline{2-4}
                            & No  & $1,0$ & $1,1$ \\ \cline{2-4}
    \end{tabular}
  \end{center}
\end{table}

\begin{parts}

  \part[10]
  Let $x=1$. 
  Graph the best-response curves of Rowena and Colin on a $p-q$ coordinate plain.
  Label all Nash equilibria in \textit{pure} and \textit{mixed} strategies.

  \part[10]
  Let $x=3$. 
  Graph the best-response curves of Rowena and Colin on a $p-q$ coordinate plain.
  Label all Nash equilibria in \textit{pure} and \textit{mixed} strategies.

  \part[4] 
  For what values of $x$ does this game have a unique Nash equilibrium?
  What is that equilibrium?

  \part[10]
  For what values of $x$ does this game have a mixed-strategy Nash equilibrium?
  With what probabiltity, expressed in terms of $x$, 
  does each player play Yes in this mixed-strategy equilibrium?

  \part[6]
  For the values of $x$ you found in part $(d)$,
  is the game an example of an \textit{assurance} game,
  a \textit{game of chicken}, or a game similar to \textit{tennis}?
  Explain.

\end{parts}

%------------------------------------------------------------------%

\newpage

\question 

Take a look at the data collected in class from 
\textbf{Activity 5 - Social Media Adspace}.
 
\begin{parts}

  \part[6]

  Find the Nash equilibrium quantity strategies for firms in terms of $a$ and $b$.

  \part[8]

  Compare your firms actual quantities produced to the equilibrium strategy function 
  in part $(a)$. Also compare the theoretical profit in equilibrium to the profits which you earned during the activity.
  Did the production behavior of firms in class match the theoretical equilibrium?
  Why or why not?

  \part[6]

  What would a monopolist firm do in this market if it didn't any competitors?
  Compare the monopolist's profit to the profits earned by firms in the activity.
  What obstacles prevented the firms from behaving like monopolists?

\end{parts}

%------------------------------------------------------------------%

\newpage

\question 

Take a look at the data collected in class from 
\textbf{Activity 6 - Penalty Shootout}.
 
\begin{parts}
  \part[6]
  Generate a testable hypothesis using mixed-strategy Nash equilibria 
  to compare against the data from our in-class activity.
  Your hypothesis should include a specific numerical value or values.
  For example, you could find the probability of a goal being scored in equilibrium,
  or the overall distribution of strategies by kickers and goalies playing equilibrium strategy profiles.

  \part[8]
  Now compare your theoretical prediction to some statistic or set of values from class.
  Do you \textit{reject} or \textit{fail to reject} the null hypothesis that the class data
  were significantly different from the theoretical distribution?
  Feel free to use any graphical, statistical, or computational tools to help your analysis.

  \part[6]
  Evaluate the predictions generated by the theory. 

  If students' behavior in class resembled equilibrium behavior, 
  under what circumstances might you expect the predictions to break down?

  If students' behavior didn't fit with the predictions, 
  what assumptions in the theory do you think failed to hold up in real life?

\end{parts}
\end{questions}

\end{document}
