## MSNE in a Larger Game
Suppose that we have this 3x2 game:

| $P_1$, $P_2$ | X (r) | Y (1 - r) |
|-------------:+-------+-----------|
|        A (p) | 2, 1  | 0, 1      |
|        B (q) | 1, 2  | 2, 0      |
|        C (z) | 0, 0  | 3, 2      |

::: {.incremental}
  * Player 1's mixed strategy uses probabilities p, q, and z, since they have three pure strategies.
:::
---

## MSNE in a Larger Game {.smaller}

::::: {.columns}
:::: {.column .smaller width="30%"}
| $P_1$, $P_2$ | X (r) | Y (1 - r) |
|:------------:+:-----:+:---------:|
|     A (p)    |  2, 1 |    0, 1   |
|     B (q)    |  1, 2 |    2, 0   |
|     C (z)    |  0, 0 |    3, 2   |
::::
:::: {.column}
Let's put together Player 1's expected payoffs:

::: {.incremental}
  * $U_1(A) = 2r + 0 = 2r$.
  * $U_1(B) = 1r + 2(1 - r) = 2 - r$.
  * $U_1(C) = 0 + 3(1 - r) = 3 - 3r$.
:::
::::
:::::
---

## MSNE in a Larger Game {.smaller}

::::: {.columns}
:::: {.column .smaller width="30%"}
| $P_1$, $P_2$ | X (r) | Y (1 - r) |
|-------------:+:-----:+:---------:|
|        A (p) |  2, 1 |    0, 1   |
|        B (q) |  1, 2 |    2, 0   |
|        C (z) |  0, 0 |    3, 2   |
::::
:::: {.column .smaller}
Next, let's see what it would take to get Player 1 to mix different pairs of strategies:

::: {.incremental}
  * A and B: $2r = 2 - r \implies r = \frac{2}{3}$.
  * A and C: $2r = 3 - 3r \implies r = \frac{3}{5}$.
  * B and C: $2 - r = 3 - 3r \implies r = \frac{1}{2}$.
:::
::::
:::::
Note that each pair of strategies requires a different value of $r$: there is no mixed strategy for Player 2 that would make Player 1 willing to mix all three of their pure strategies.

---

## MSNE in a Larger Game {.smaller}

::::: {.columns}
:::: {.column width="30%"}
| $P_1$, $P_2$ | X (r) | Y (1 - r) |
|--------------+-------+-----------|
| A (p)        | 2, 1  | 0, 1      |
| B (q)        | 1, 2  | 2, 0      |
| C (z)        | 0, 0  | 3, 2      |
::::
:::: {.column}
Let's check Player 2's expected payoffs next:

::: {.incremental}
  * $U_2(X) = 1p + 2q + 0$.
  * $U_2(Y) = 1p + 0 + 2(z)$.
  * So Player 2 will play a mixed strategy if $p + 2q = p + 2(z) \implies q = z$.
  * There are two ways that this can be true: Either Player 1 plays B and C
  with equal probability (and we know from earlier that they would **only** be
  playing these two, not A), or Player 1 plays A only, and B and C not at all. 
:::
::::
:::::
---

## MSNE in a Larger Game {.smaller}
So, one type of MSNE is where Player 1 only plays A: 

this requires $2r \geq 2 - r$ and $2r \geq 3 - 3r \Rightarrow r \geq \frac{2}{3}$ and $r \geq \frac{3}{5}$.

::: {.incremental}
  * MSNE: $(1, 0, 0), (r, 1 - r)$, where $r \geq \frac{2}{3}$.
  * And the other type of MSNE is where Player 1 plays B and C with equal (1/2)
    probability, and Player 2 plays X and Y with equal (1/2) probability.
  * MSNE: $(0, 1/2, 1/2), (1/2, 1/2)$
:::
---

## Graph Player 1's expected utilities

```{r}
#| echo: false
library(ggplot2)
library(latex2exp)
# define expected utility functions
EU1_A = function(r) {2*r + 0}
EU1_B = function(r) {1*r + 2*(1-r)}
EU1_C = function(r) {0 + 3*(1-r)}
# define range for r
r_values <- seq(0, 1, length.out = 100)
# Compute the expected utilities for each value of p
utilities1_A <- EU1_A(r_values)
utilities1_B <- EU1_B(r_values)
utilities1_C <- EU1_C(r_values)

data_1 <- data.frame(
  r = r_values,
  A = utilities1_A,
  B = utilities1_B,
  C = utilities1_C
)
# Plot the expected utilities and indicate the best response threshold
EU1_plot <- ggplot(data_1, aes(x = r)) +
  geom_line(aes(y = A, color = "EU_1(A)"), linewidth = 2) +
  geom_line(aes(y = B, color = "EU_1(B)"), linewidth = 2) +
  geom_line(aes(y = C, color = "EU_1(C)"), linewidth = 2) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 0.6, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 2/3, linetype = "dashed", color = "grey50") +
  labs(title = "Player 1's Expected Utilities",
       x = "Probability of X (r)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
EU1_plot 
```
  * If $q<z$ then $BR_2 = \{X\}$
  * If $q>z$ then $BR_2 = \{Y\}$
  * If $q=z$ then $BR_2 = \{X,Y,(r)\}$

---

## When will Player 1 mix? {.smaller}
What it would take to get Player 1 to mix different pairs of strategies:

::: {.incremental}
  * A and B: $2r = 2 - r \implies r = \frac{2}{3}$.
  * A and C: $2r = 3 - 3r \implies r = \frac{3}{5}$.
  * B and C: $2 - r = 3 - 3r \implies r = \frac{1}{2}$.
    * Note that there is no intersection between all three lines simultaneously
    * This means that Player 1 will never mix between all three strategies
:::
---

## MSNE in a Larger Game
Let's check Player 2's expected payoffs next:

::: {.incremental}
  * $U_2(X) = 1p + 2q + 0$.
  * $U_2(Y) = 1p + 0 + 2(z)$.
  * So Player 2 will play a mixed strategy if
  $$p + 2q = p + 2(z)$$ 
  $$\implies q = z$$.

  * Recall that $q$ was the probability we put on Player 2 playing $B$,
  * and $z$ was the probability they play $C$. 
:::

---

## visualizing Player 2's Best Responses
```{r}
#| echo: false
#| message: false
# install.packages("ggtern")
library(ggtern)

data <- tidyr::tibble(
  p = runif(100),
  q = seq(0, 1, length.out = 100),
  z = seq(0, 1, length.out = 100)
)
EU2_plot <- ggtern(data, aes(x=p, y=q, z=z, color = "Indifference: q = z")) +
  geom_path(linewidth = 2) +
  theme_rgbw()
EU2_plot
```
---

## When will Player 2 mix? {.smaller}
We found they are indifferent between $X$ and $Y$ when 
$$ q = 1 - p - d $$.

There are two ways that this can be true: 

::: {.incremental}
  * Either Player 1 plays B and C with equal probability
  (and we know from earlier that they would **only** be playing these two, not A),
  * or Player 1 plays A only, and B and C not at all. 
:::

---

## MSNE in a Larger Game {.smaller}
<u>Case 1</u>: Player 1 only plays A:

::::: {.columns}
:::: {.column}
::: {.incremental}
  * this requires $2r \geq 2 - r$ and $2r \geq 3 - 3r$,
  * which imply that $r \geq \frac{2}{3}$ and $r \geq \frac{3}{5}$.
  * **MSNE 1:** 
    + $\sigma_1 = (p = 1, q = 0, z = 0),$
    + $\sigma_2 = (r, 1 - r)$ where $r \geq \frac{2}{3}$.
:::
::::
:::: {.column}
```{r}
#| echo: false
EU1_plot
```
::::
:::::
---

## MSNE in a Larger Game {.smaller}
<u>Case 2</u>: Player 1 plays $B$ and $C$ with equal probability 

::::: {.columns}
:::: {.column}
::: {.incremental}
  * then Player 2 plays X and Y with equal (1/2) probability.
  * **MSNE**: $\sigma_1 = (p = 0, q = 1/2, z = 1/2), \sigma_2 = (1/2, 1/2)$
::: 
::::
:::: {.column}
```{r}
#| echo: false
EU2_plot
```
::::
:::::
---

## Solving MSNE in a 3x3 Game

| $P_1$, $P_2$ |  Left | Center | Right |
|-------------:+:-----:+:------:+:-----:|
|          Top | 2,  1 |  3,  0 | 3,  0 |
|       Middle | 3,  0 |  0,  1 | 3,  0 |
|       Bottom | 3,  0 |  3,  0 | 2,  1 |

Any *pure* strategy NE?

---

## Solving for 3-strategy MSNE

**Step 1:** Define Mixed Strategies

::: {.incremental}
  * <u>Player 1's mixed strategy:</u> 
  Let $\sigma_1 = (t, m, b)$  

  * <u>Player 2's mixed strategy:</u> 
  Let $\sigma_2 = (\ell, c, r)$  
:::
  
Note that the lowercase letters represent the probabilities played
on the uppercase pure strategies.

---

## Solving for 3-strategy MSNE {.smaller}
**Step 2:** Solve for Expected Utilities

:::: {.columns}
::: {.column}
  * <u>Player 1:</u>
    + $EU_1(T, \sigma_2) = 2\ell + 3c + 3r$
    + $EU_1(M, \sigma_2) =  3\ell + 3r$
    + $EU_1(B, \sigma_2) = 3\ell + 3c + 2r$
:::
::: {.column}
  * <u>Player 2:</u>
    * $EU_2(L, \sigma_1) = t$
    * $EU_2(C, \sigma_1) = m$
    * $EU_2(R, \sigma_1) = b$
:::
::::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 3:** Find Indifference Conditions

<u>When will Player 1 mix between 2 pure strategies?</u>

* When does $EU_1(Top, \sigma_2) \geq EU_1(Middle, \sigma_2)$:

  $$
  \begin{align}
  2\ell + 3c + 3r & \geq 3\ell + 3r \\ 
  \Rightarrow 3c & \geq \ell
  \end{align}
  $$

* When does $EU_1(Top, \sigma_2) \geq EU_1(Bottom, \sigma_2)$:

  $$
  \begin{align}
  2\ell + 3c + 3r & \geq 3\ell + 3c + 2r \\ 
  \Rightarrow r & \geq \ell
  \end{align}
  $$

* When does $EU_1(Middle, \sigma_2) \geq EU_1(Bottom, \sigma_2)$:

  $$
  \begin{align}
  3\ell + 3r & \geq 3\ell + 3c + 2r \\ 
  \Rightarrow r & \geq 3c
  \end{align}
  $$
    
---


## Solving for 3-strategy MSNE

**Step 3:** Find Indifference Conditions

<u>When will Player 2 mix between 2 pure strategies?</u> 

  * When does $EU_2(Left, \sigma_1) \geq EU_2(Center, \sigma_1)$:
  $$ t \geq m $$
  * When does $EU_2(Left, \sigma_1) = EU_2(Right, \sigma_1)$:
  $$ t \geq b $$
  * When does $EU_2(Center, \sigma_1) = EU_2(Right, \sigma_1)$:
  $$ m \geq b $$
  
---


## Solving for 3-strategy MSNE

**Step 4:** Check Cases for possible Nash Equilibria:

| $P_1$, $P_2$ |  Left | Center | Right |
|-------------:+:-----:+:------:+:-----:|
|          Top | 2,  1 |  3,  0 | 3,  0 |
|       Middle | 3,  0 |  0,  1 | 3,  0 |
|       Bottom | 3,  0 |  3,  0 | 2,  1 |

Any cases where either player plays only *one* pure strategy?

::: {.incremental}
  * No! We already checked for PSNE in the table
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 1: Player 2 mixes between **Left** and **Center**</u>

Then we know that $EU_2(\text{Left}) = EU_2(\text{Center}) > EU_2(R)$ 

::: {.incremental}
$$ \Rightarrow t = m > b$$

  * If $\ell > 3/4$ then $BR_1 = \{\text{Middle}\} \Rightarrow m = 1$
    + **contradiction:** $m$ can't be equal to $t$ and also sum to 1
  * If $\ell < 3/4$ then $BR_1 = \{\text{Top}\} \Rightarrow t = 1$
    + **contradiction:** $t$ can't be equal to $m$ and also sum to 1
  * If $\ell = 3/4$ then $BR_1 = (t, m, 0)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 1/2, m = 1/2, b = 0)$, 
  $\sigma_2 = (\ell = 3/4, c = 1/4, r = 0) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 2: Player 2 mixes between **Left** and **Right**</u>

Then we know that $EU_2(\text{Left}) = EU_2(\text{Right}) > EU_2(Center)$ 

::: {.incremental}
$$ \Rightarrow t = b > m$$

  * If $\ell > 1/2$ then $BR_1 = \{\text{Bottom}\} \Rightarrow b = 1$
    + **contradiction:** $b$ can't be equal to $t$ and also sum to 1
  * If $\ell < 1/2$ then $BR_1 = \{\text{Top}\} \Rightarrow t = 1$
    + **contradiction:** $t$ can't be equal to $b$ and also sum to 1
  * If $\ell = 1/2$ then $BR_1 = (t, 0, b)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 1/2, m = 0, b = 1/2)$, 
  $\sigma_2 = (\ell = 1/2, c = 0, r = 1/2) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 3: Player 2 mixes between **Center** and **Right**</u>

Then we know that $EU_2(\text{Center}) = EU_2(\text{Right}) > EU_2(Left)$ 

::: {.incremental}
$$ \Rightarrow m = b > t$$

  * If $r > 3/4$ then $BR_1 = \{\text{Middle}\} \Rightarrow m = 1$
    + **contradiction:** $m$ can't be equal to $b$ and also sum to 1
  * If $r < 3/4$ then $BR_1 = \{\text{Bottom}\} \Rightarrow b = 1$
    + **contradiction:** $b$ can't be equal to $m$ and also sum to 1
  * If $r = 3/4$ then $BR_1 = (0, m, b)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 0, m = 1/2, b = 1/2)$, 
  $\sigma_2 = (\ell = 0, c = 1/4, r = 3/4) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 4: Player 2 mixes between **Left**, **Center**, and **Right**</u>

Then we know that $EU_2(\text{Center}) = EU_2(\text{Right}) = EU_2(Left)$ 

::: {.incremental}
$$ \Rightarrow t = m = b$$

$$ \Rightarrow \ell = 3c = r$$

And because probabilities must sum to one:

$$
\begin{align}
3c + c + 3c & = 1 \\
\Rightarrow 7c & = 1 \\
c & = 1/7
\end{align}
$$

$\{ \sigma_1 = (t = 1/3, m = 1/3, b = 1/3),$
$\sigma_2 = (\ell = 3/7, c = 1/7, r = 3/7) \}$ is an MSNE
:::

