# Mixed strategies in larger games

## MSNE in a Larger Game
Suppose that we have this 3x2 game:

| $P_1$, $P_2$ | X (r) | Y (1 - r) |
|-------------:+-------+-----------|
| A ($\alpha$) | 2, 1  | 0, 1      |
| B ($\beta$)  | 1, 2  | 2, 0      |
| C ($\gamma$) | 0, 0  | 3, 2      |

  * Player 1's mixed strategy uses probabilities $\alpha, \beta, \gamma$ since they have three pure strategies.
    + You could also replace $\gamma$ with $(1-\alpha-\beta)$
      - because lotter probabilites sum to one
  * Player 2 just has two pure strategies w/ probability $r$ of $X$

---

## 3-Strategy Player's Payoffs

Let's put together Player 1's expected payoffs:

| $P_1$, $P_2$ | X ($r$) | Y ($1-r$)|
|:------------:+:-----:+:---------:|
| A  | 2, 1  | 0, 1      |
| B  | 1, 2  | 2, 0      |
| C  | 0, 0  | 3, 2      |

They have three discrete strategies to choose from:

::: {.incremental}
  * $EU_1(A) = 2r + 0 = 2r$.
  * $EU_1(B) = 1r + 2(1 - r) = 2 - r$.
  * $EU_1(C) = 0 + 3(1 - r) = 3 - 3r$.
:::

---

## 3-strategy Player's Indifference

When would Player 1 want to play different strategies?

::: {.incremental}
  * Indifferent between A and B: $2r = 2 - r \implies r = \frac{2}{3}$.
  * Indifferent between A and C: $2r = 3 - 3r \implies r = \frac{3}{5}$.
  * Indifferent between B and C: $2 - r = 3 - 3r \implies r = \frac{1}{2}$.
    - Note that each pair of strategies requires a different value of $r$:
      + never willing to mix all three of their pure strategies.
:::

---

## Graph Player 1's expected utilities

```{r}
#| echo: false
library(ggplot2)
library(latex2exp)
# define expected utility functions
EU1_A = function(r) {2*r + 0}
EU1_B = function(r) {1*r + 2*(1-r)}
EU1_C = function(r) {0 + 3*(1-r)}
# define range for r
r_values <- seq(0, 1, length.out = 100)
# Compute the expected utilities for each value of p
utilities1_A <- EU1_A(r_values)
utilities1_B <- EU1_B(r_values)
utilities1_C <- EU1_C(r_values)

data_1 <- data.frame(
  r = r_values,
  A = utilities1_A,
  B = utilities1_B,
  C = utilities1_C
)
# Plot the expected utilities and indicate the best response threshold
EU1_plot <- ggplot(data_1, aes(x = r)) +
  geom_line(aes(y = A, color = "EU_1(A)"), linewidth = 2) +
  geom_line(aes(y = B, color = "EU_1(B)"), linewidth = 2) +
  geom_line(aes(y = C, color = "EU_1(C)"), linewidth = 2) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 0.6, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 2/3, linetype = "dashed", color = "grey50") +
  labs(title = "Player 1's Expected Utilities",
       x = "Probability of X (r)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
EU1_plot 
```

* If $r<0.5$ then $BR_1 = \{C\}$
* If $r=0.5$ then $BR_1 = \{B,C\}$
* If $0.5<r<0.\bar{6}$ then $BR_1 = \{B\}$
* If $r=0.\bar{6}$ then $BR_1 = \{A,B\}$
* If $0.\bar{6}<r$ then $BR_1 = \{A\}$

---

## When will Player 1 mix?
What it would take to get Player 1 to mix different pairs of strategies:

::: {.incremental}
  * A and B: $2r = 2 - r \implies r = \frac{2}{3}$.
  * A and C: $2r = 3 - 3r \implies r = \frac{3}{5}$.
  * B and C: $2 - r = 3 - 3r \implies r = \frac{1}{2}$.
    * Note that there is no intersection between all three lines simultaneously
    * This means that Player 1 will never mix between all three strategies
:::
---

## Two-Strat Player's Indifference

| $P_1$, $P_2$ | X  | Y  |
|--------------+-------+-----------|
| A ($\alpha$) | 2, 1  | 0, 1      |
| B ($\beta$)  | 1, 2  | 2, 0      |
| C ($\gamma$) | 0, 0  | 3, 2      |

Let's check Player 2's expected payoffs next:

::: {.incremental}
  * They only have two pure strats, but have to react to three different probabilities
  * $U_2(X) = 1\alpha + 2\beta + 0\gamma$.
  * $U_2(Y) = 1\alpha + 0\beta + 2\gamma$.
:::

---

## MSNE in a Larger Game
Let's check Player 2's expected payoffs next:

::: {.incremental}
  * $U_2(X) = 1\alpha + 2\beta + 0$.
  * $U_2(Y) = 1\alpha + 0 + 2\gamma$.
  * [Opponent's Indifference Condition]{.hi}:
    - Player 2 will mix if $\alpha + 2\beta = \alpha + 2\gamma \implies \beta = \gamma$.
    - Examples of when this can be true: 
      + Either Player 1 plays B and C equally
      + or Player 1 plays A only, and B and C not at all. 
:::

---

## visualizing Player 2's Best Responses
```{r}
#| echo: false
#| message: false
# install.packages("ggtern")
library(ggtern)

data <- tidyr::tibble(
  a = runif(100),
  b = seq(0, 1, length.out = 100),
  c = seq(0, 1, length.out = 100)
)
EU2_plot <- ggtern(data, aes(x=b, y=a, z=c, color = "Indifference: b = c")) +
  geom_path(linewidth = 2) +
  theme_rgbw()
EU2_plot
```

  * If $\beta<\gamma$ then $BR_2 = \{X\}$
  * If $\beta>\gamma$ then $BR_2 = \{Y\}$
  * If $\beta=\gamma$ then $BR_2 = \{X,Y\}$
    + AKA they would be willing to mix between $X$ and $Y$ with prob $r$

---

## Checking for all MSNE

There might be multiple MSNE

* How can we make sure we find them all?

  + Check case-by-case

  + I'll use the ranges of $r$ to check for any BR intersections

## Checking for all MSNE
<u>Case 1</u>: $r>2/3$:

::::: {.columns}
:::: {.column}
::: {.incremental}
  * Player 1 only plays **A**
  * Player 2 is indifferent between **X** and **Y**
    + because $\beta=\gamma=0$
    + So player 2 will be willing to mix
  * **MSNE 1:** 
    + $\sigma_1 = (\alpha = 1, \beta = 0, \gamma = 0),$
    + $\sigma_2 = (r, 1 - r)$ where $r \geq \frac{2}{3}$.
:::
::::
:::: {.column}
| $P_1$, $P_2$ | X  | Y  |
|--------------+----+----|
| A       | <u>2</u>, <u>1</u>  | 0, <u>1</u> |
| B       | 1, 2  | 2, 0 |
| C       | 0, 0  | 3, 2 |
::::
:::::
---

## Checking for all MSNE
<u>Case 2</u>: $r=2/3$:

::::: {.columns}
:::: {.column width="60%"}
::: {.incremental}
  * Player 1 is indifferent betwen **A** and **B**
    + Never plays **C**
  * Player 2 won't mix if $\beta\neq \gamma =0$
  * **MSNE 1:** 
    + $\sigma_1 = (1, 0, 0),$
    + $\sigma_2 = (\frac{2}{3}, \frac{1}{3})$ 
  * This is just a subcase of **MSNE 1**
:::
::::
:::: {.column width="40%"}
| $P_1$, $P_2$ | X  | Y  |
|--------------+----+----|
| A       | <u>2</u>, <u>1</u>  | 0, <u>1</u> |
| B       | 1, 2  | 2, 0 |
| C       | 0, 0  | 3, 2 |
::::
:::::
---

## Checking for all MSNE
<u>Case 3</u>: $\frac{1}{2}<r<\frac{2}{3}$ 

::::: {.columns}
:::: {.column}
::: {.incremental}
  * then Player 1 plays only **B**
  * But if $\beta=1$ then $\gamma \neq \beta$
    + Player 2 is no longer indifferent
    + They would rather play only **X**
  * No MSNE here
::: 
::::
:::: {.column}
```{r}
#| echo: false
EU1_plot
```
::::
:::::

---

## Checking for all MSNE
<u>Case 4</u>: $r=\frac{1}{2}$ 

::::: {.columns}
:::: {.column}
::: {.incremental}
  * Player 1 mixes between **B** and **C**
    + But never plays **A** ($\alpha=0$)
  * Player 2 will mix if $\beta=\gamma$
  * **MSNE 2**: 
    + $\sigma_1 = (\alpha = 0, \beta = 1/2, \gamma = 1/2)$,
    + $\sigma_2 = (1/2, 1/2)$
::: 
::::
:::: {.column}
```{r}
#| echo: false
EU1_plot
```
::::
:::::
---

## Checking for all MSNE
<u>Case 5</u>: $r<\frac{1}{2}$ 

::::: {.columns}
:::: {.column}
::: {.incremental}
  * Player 1 only plays **C**
  * Player 2's best response is only **Y**
  * **MSNE 3**: 
    + $\sigma_1 = (\alpha = 0, \beta = 0, \gamma = 1)$,
    + $\sigma_2 = (0, 1)$
  * This is also a *pure strategy* Nash
::: 
::::
:::: {.column}
| $P_1$, $P_2$ | X  | Y  |
|--------------+----+----|
| A       | 2, 1  | 0, 1 |
| B       | 1, 2  | 2, 0 |
| C       | 0, 0  | <u>3</u>, <u>2</u> |
::::
:::::
---

## MSNE in 3x2 Game

So across all cases, we found:

* Two pure strategy Nash:
  + $\{A, X\}$
  + $\{C, Y\}$
* One MSNE where both player mix:
  + $\{(0A, 1/2 B, 1/2 C),~ (1/2 X, 1/2 Y)\}$
* Another MSNE when only Player 2 mixes:
  + $\{(1A, 0 B, 0 C),~ (r X, (1-r) Y)\}$ where $r \geq 2/3$
    - (includes PSNE $\{A, X\}$)

---

## Solving MSNE in a 3x3 Game

| $P_1$, $P_2$ |  Left | Center | Right |
|-------------:+:-----:+:------:+:-----:|
|          Top | 2,  1 |  3,  0 | 3,  0 |
|       Middle | 3,  0 |  0,  1 | 3,  0 |
|       Bottom | 3,  0 |  3,  0 | 2,  1 |

Any *pure* strategy NE?

---

## Solving for 3-strategy MSNE

**Step 1:** Define Mixed Strategies

::: {.incremental}
  * <u>Player 1's mixed strategy:</u> 
  Let $\sigma_1 = (t, m, b)$  

  * <u>Player 2's mixed strategy:</u> 
  Let $\sigma_2 = (\ell, c, r)$  
:::
  
Note that the lowercase letters represent the probabilities played
on the uppercase pure strategies.

---

## Solving for 3-strategy MSNE 
**Step 2:** Solve for Expected Utilities

:::: {.columns}
::: {.column}
  * <u>Player 1:</u>
    + $EU_1(T, \sigma_2) = 2\ell + 3c + 3r$
    + $EU_1(M, \sigma_2) =  3\ell + 3r$
    + $EU_1(B, \sigma_2) = 3\ell + 3c + 2r$
:::
::: {.column}
  * <u>Player 2:</u>
    * $EU_2(L, \sigma_1) = t$
    * $EU_2(C, \sigma_1) = m$
    * $EU_2(R, \sigma_1) = b$
:::
::::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 3:** Find Indifference Conditions

<u>When will Player 1 mix between 2 pure strategies?</u>

* When does $EU_1(Top, \sigma_2) \geq EU_1(Middle, \sigma_2)$:

  $$
  \begin{align}
  2\ell + 3c + 3r & \geq 3\ell + 3r \\ 
  \Rightarrow 3c & \geq \ell
  \end{align}
  $$

* When does $EU_1(Top, \sigma_2) \geq EU_1(Bottom, \sigma_2)$:

  $$
  \begin{align}
  2\ell + 3c + 3r & \geq 3\ell + 3c + 2r \\ 
  \Rightarrow r & \geq \ell
  \end{align}
  $$

* When does $EU_1(Middle, \sigma_2) \geq EU_1(Bottom, \sigma_2)$:

  $$
  \begin{align}
  3\ell + 3r & \geq 3\ell + 3c + 2r \\ 
  \Rightarrow r & \geq 3c
  \end{align}
  $$
    
---


## Solving for 3-strategy MSNE

**Step 3:** Find Indifference Conditions

<u>When will Player 2 mix between 2 pure strategies?</u> 

  * When does $EU_2(Left, \sigma_1) \geq EU_2(Center, \sigma_1)$:
  $$ t \geq m $$
  * When does $EU_2(Left, \sigma_1) = EU_2(Right, \sigma_1)$:
  $$ t \geq b $$
  * When does $EU_2(Center, \sigma_1) = EU_2(Right, \sigma_1)$:
  $$ m \geq b $$
  
---


## Solving for 3-strategy MSNE

**Step 4:** Check Cases for possible Nash Equilibria:

| $P_1$, $P_2$ |  Left | Center | Right |
|-------------:+:-----:+:------:+:-----:|
|          Top | 2,  1 |  3,  0 | 3,  0 |
|       Middle | 3,  0 |  0,  1 | 3,  0 |
|       Bottom | 3,  0 |  3,  0 | 2,  1 |

Any cases where either player plays only *one* pure strategy?

::: {.incremental}
  * No! We already checked for PSNE in the table
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 1: Player 2 mixes between **Left** and **Center**</u>

Then we know that $EU_2(\text{Left}) = EU_2(\text{Center}) > EU_2(R)$ 

::: {.incremental}
$$ \Rightarrow t = m > b$$

  * If $\ell > 3/4$ then $BR_1 = \{\text{Middle}\} \Rightarrow m = 1$
    + **contradiction:** $m$ can't be equal to $t$ and also sum to 1
  * If $\ell < 3/4$ then $BR_1 = \{\text{Top}\} \Rightarrow t = 1$
    + **contradiction:** $t$ can't be equal to $m$ and also sum to 1
  * If $\ell = 3/4$ then $BR_1 = (t, m, 0)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 1/2, m = 1/2, b = 0)$, 
  $\sigma_2 = (\ell = 3/4, c = 1/4, r = 0) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 2: Player 2 mixes between **Left** and **Right**</u>

Then we know that $EU_2(\text{Left}) = EU_2(\text{Right}) > EU_2(Center)$ 

::: {.incremental}
$$ \Rightarrow t = b > m$$

  * If $\ell > 1/2$ then $BR_1 = \{\text{Bottom}\} \Rightarrow b = 1$
    + **contradiction:** $b$ can't be equal to $t$ and also sum to 1
  * If $\ell < 1/2$ then $BR_1 = \{\text{Top}\} \Rightarrow t = 1$
    + **contradiction:** $t$ can't be equal to $b$ and also sum to 1
  * If $\ell = 1/2$ then $BR_1 = (t, 0, b)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 1/2, m = 0, b = 1/2)$, 
  $\sigma_2 = (\ell = 1/2, c = 0, r = 1/2) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 3: Player 2 mixes between **Center** and **Right**</u>

Then we know that $EU_2(\text{Center}) = EU_2(\text{Right}) > EU_2(Left)$ 

::: {.incremental}
$$ \Rightarrow m = b > t$$

  * If $r > 3/4$ then $BR_1 = \{\text{Middle}\} \Rightarrow m = 1$
    + **contradiction:** $m$ can't be equal to $b$ and also sum to 1
  * If $r < 3/4$ then $BR_1 = \{\text{Bottom}\} \Rightarrow b = 1$
    + **contradiction:** $b$ can't be equal to $m$ and also sum to 1
  * If $r = 3/4$ then $BR_1 = (0, m, b)$
    + No contradiction! 
  * So $\{ \sigma_1 = (t = 0, m = 1/2, b = 1/2)$, 
  $\sigma_2 = (\ell = 0, c = 1/4, r = 3/4) \}$ is an MSNE
:::

---

## Solving for 3-strategy MSNE {.smaller}

**Step 4:** Check Cases for possible Nash Equilibria:

<u>Case 4: Player 2 mixes between **Left**, **Center**, and **Right**</u>

Then we know that $EU_2(\text{Center}) = EU_2(\text{Right}) = EU_2(Left)$ 

::: {.incremental}
$$ \Rightarrow t = m = b$$

$$ \Rightarrow \ell = 3c = r$$

And because probabilities must sum to one:

$$
\begin{align}
3c + c + 3c & = 1 \\
\Rightarrow 7c & = 1 \\
c & = 1/7
\end{align}
$$

$\{ \sigma_1 = (t = 1/3, m = 1/3, b = 1/3),$
$\sigma_2 = (\ell = 3/7, c = 1/7, r = 3/7) \}$ is an MSNE
:::

