# More MSNE Examples
```{r}
#| echo: false
library(tidyverse)
library(ggplot2)
library(tidyverse)
library(latex2exp)

knitr::opts_chunk$set(
    out.width = "70%", # enough room to breath
    fig.width = 6,     # reasonable size
    fig.asp = 0.618,   # golden ratio
    fig.align = "center" # mostly what I want
)
```

## Practice your understanding 
Consider the following game table. What are **Player 1's** expected payoffs, given Player 2's mixed strategy?

| $P_1$, $P_2$   | Up $(q)$ | Down $(1 - q)$ |
|---------------:+:--------:+:--------------:|
| Up $(p)$       | 2, -2    | -3, 3          |
| Down $(1 - p)$ | -5, 5    | 1, -1          |

::: {.incremental}
  * $U_1(Up) = 2q -3(1-q) = 5q - 3$,
  * $U_1(Down) = -5q + 1(1-q) = -6q +1$
:::

---

## Practice your understanding 
Consider the following game table. What are **Player 2's** expected payoffs, given Player 1's mixed strategy?

| $P_1$, $P_2$   | Up $(q)$ | Down $(1 - q)$ |
|---------------:+:--------:+:--------------:|
| Up $(p)$       | 2, -2    | -3, 3          |
| Down $(1 - p)$ | -5, 5    | 1, -1          |

::: {.incremental}
* $U_2(Up) = -2p + 5(1-p) = -7p + 5$,
* $U_2(Down) = 3p - 1(1-p) = 4p -1$
:::

---

## Practice your understanding

The correct answers to the previous two questions were:

  * $U_1(Up) = 5q - 3$
  * $U_1(Down) = -6q + 1 $.
  * $U_2(Up) = -7p + 5$
  * $U_2(Down) = 4p - 1$.

Based on this, what are $p$ and $q$ in the MSNE of this game?

::: {.incremental}
  * $p^* = 6/11$
  * $q^* = 4/11$
:::

---

## Multiple MSNE in one game 

Consider the following game table:

::::: {.columns}
:::: {.column}
| $P_1$, $P_2$ | $X~(q)$ | $Y~(1 - q)$ |
|-------------:+:-------:+:-----------:|
| $A~(p)$      | 2, 2    | 3, 2        |
| $B~(1 - p)$  | 4, 3    | 0, 0        |
::::

:::: {.column}
The players' expected payoffs are:

::: {.incremental}
$$
\begin{align*}
U_1(A) & = 2q + 3(1 - q) \\
       & = 2q + 3 - 3q \\
       & = 3 - q \\
U_1(B) & = 4q + 0(1 - q) \\
       & = 4q \\
U_2(X) & = 2p + 3(1 - p) \\
       & = 2p + 3 - 3p \\
       & = 3 - p \\
U_2(Y) & = 2p + 0(1 - p) \\
       & = 2p
\end{align*}
$$
:::
::::
:::::
---

## Multiple MSNE in one game {.smaller}

Based on this, the conditions under which each player will use a mixed strategy are:

$$
\begin{align*}
Player~1: && Player~2:&\\
3 - q &= 4q & 3 - p &= 2p\\
3 &= 5q & 3 &= 3p\\
q &= 3/5 & p &= 1
\end{align*}
$$

::: {.incremental}
  * We've never seen anything like $p = 1$ in this context before...
  * **Player 2 will only mix** if **Player 1 only plays A**
  * This usually occurs when one strategy **weakly** dominates another.
:::
---

## Multiple MSNE in one game
:::: {.columns}
::: {.column}
```{r}
#| echo: false
U1_A <- function(q) {
  2*q + 3*(1-q)
}
U1_B <- function(q) {
  4*q + 0*(1-q)
}
# Generate a sequence of values for p from 0 to 1
p_values <- seq(0, 1, length.out = 100)
# Compute the expected utilities for each value of p
utilities1_A <- U1_A(p_values)
utilities1_B <- U1_B(p_values)
# Create a data frame for plotting
data_1 <- data.frame(p = p_values, A = utilities1_A, B = utilities1_B)
# Plot the expected utilities and indicate the best response threshold
ggplot(data_1, aes(x = p)) +
  geom_line(aes(y = A, color = "Exp. Util. of A (3 - q)"), linewidth = 2) +
  geom_line(aes(y = B, color = "Exp. Util. of B (4q)"), linewidth = 2) +
  geom_vline(xintercept = 3/5, linetype = "dashed", color = "grey50") +
  annotate("text", x = 3/5, y = 0, label = "q = 3/5", hjust = -0.1, color = "grey50") +
  labs(title = "Player 1's Expected Utilities",
       x = "Probability of X (q)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```
:::
::: {.column}
```{r}
#| echo: false
U2_X <- function(p) {
  2*p + 3*(1-p)
}
U2_Y <- function(p) {
  2*p + 0*(1-p)
}
# Generate a sequence of values for p from 0 to 1
q_values <- seq(0, 1, length.out = 100)
# Compute the expected utilities for each value of p
utilities2_X <- U2_X(q_values)
utilities2_Y <- U2_Y(q_values)
# Create a data frame for plotting
data_2 <- data.frame(q = q_values, X = utilities2_X, Y = utilities2_Y)
# Plot the expected utilities and indicate the best response threshold
ggplot(data_2, aes(x = q)) +
  geom_line(aes(y = X, color = "Exp. Util. of X (3 - p)"), linewidth = 2) +
  geom_line(aes(y = Y, color = "Exp. Util. of Y (2q)"), linewidth = 2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  labs(title = "Player 2's Expected Utilities",
       x = "Probability of A (p)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```
:::
::::

## Multiple MSNE in one game {.smaller}
We can still approach this the same way that we have in the past:

::::: {.columns}
:::: {.column width="30%"}
| $P_1$, $P_2$ | $X~(q)$ | $Y~(1 - q)$ |
|-------------:+:-------:+:-----------:|
| $A~(p)$      | 2, 2    | 3, 2        |
| $B~(1 - p)$  | 4, 3    | 0, 0        |
::::

:::: {.column}
::: {.incremental}
  * Suppose in MSNE that Player 1 plays a (non-trivial) mixed strategy.
  * Then Player 2 must also play a mixed strategy, in which q = 3/5.
    + But Player 2 will only mix if Player 1 plays  p = 1, which is a trivial mixed strategy. 
    + This is a contradiction, **there is no MSNE where Player 1 plays a non-trivial mixed strategy**
:::
::::
:::::
---

## Multiple MSNE in one game {.smaller}
Approach it the other way next:

::::: {.columns}
:::: {.column width="30%"}
| $P_1$, $P_2$ | $X~(q)$ | $Y~(1 - q)$ |
|-------------:+:-------:+:-----------:|
| $A~(p)$      | 2, 2    | 3, 2        |
| $B~(1 - p)$  | 4, 3    | 0, 0        |
::::

:::: {.column}
Suppose Player 2 plays a non-trivial mixed strategy.

::: {.incremental}
  * Then Player 1 must play A as a pure strategy.
  * Player 2 will play A if $3 - q \geq 4q$, i.e. if $3/5 \geq q$.
  * This lets Player 2 play a non-trivial mixed strategy! There is no contradiction here.
:::
::::
:::::
---

## Multiple MSNE in one game {.smaller}
::: {.incremental}
  * There are a range of MSNEs here: all strategy profiles $(1, 0), (q, 1 - q)$, in which $q \in (0, 3/5]$
  * There are also two trivial MSNEs, $(1, 0), (0, 1)$ and $(0, 1), (1, 0)$, 
    which are really just the pure-strategy Nash equilibria (A, Y) and (B, X) expressed in the form of an MSNE.
  * It will help to understand what's going on with the Best Responses graph:
:::
---

## Multiple MSNE in one game
 
```{r}
#| code-fold: true
#| warning: false

# Create a data frame for plotting
data <- data.frame(
  q = c(0, 3/5, 3/5, 1),
  BR1 = c(1, 1, 0, 0),
  p = c(1, 0, 0, 0),
  BR2 = c(0, 1, 1, 1)
)

# Plot the best response functions
ggplot(data) +
  geom_step(aes(x = q, y = BR1, color = "BR_1"), direction = "hv", linewidth = 2, alpha = 0.9) +
  geom_step(aes(x = BR2, y = p, color = "BR_2"), direction = "vh", linewidth = 2, alpha = 0.9) +
  geom_segment(aes(x = 3/5, xend = 1, y = 0, yend = 0, color = "MSNE"), linewidth = 1.5, linetype = "dotted") +
  geom_point(aes(x=0, y=1, color = "PSNE"), size = 2) +
  geom_point(aes(x=1, y=0, color = "PSNE"), size = 2) +
  labs(title = "Best Response Functions for Mixed Strategy Nash Equilibrium",
       x = "q",
       y = "p",
       color = "Best Response") +
  theme_minimal()
```

---

## Absence of MSNEs {.smaller}

Let us return to the Prisoner's Dilemma and check for MSNEs:

| Guido, Luca        | $Testify~(q)$ | $Keep~Quiet~(1-q)$ |
|--------------------+---------------+--------------------|
| $Testify~(p)$      | $-10,-10$     | $0,-20$            |
| $Keep~Quiet~(1-p)$ | $-20,0$       | $-1,-1$            |

Guido and Luca's expected payoffs are:

::: {.incremental}
  * $U_G(Testify) = -10q + 0(1 - q) = -10q$.
  * $U_G(Keep Quiet) = -20q + (-1)(1 - q) = -1 - 19q$.
  * $U_L(Testify) = -10p + 0(1 - p) = -10p$.
  * $U_L(Keep Quiet) = -20p + (-1)(1 - p) = -1 - 19p$.
:::
---

## Absence of MSNEs {.smaller}
Guido will play a mixed strategy if:

$$
\begin{align*}
-10q &= -1 - 19q\\
9q &= -1\\
q &= -1/9
\end{align*}
$$

::: {.incremental}
  * But **-1/9 is not a valid probability!**
  * We could also note that if $q\in [0, 1]$:
    + $-10q$ is always greater than $-1 - 19q$.
  * In other words, as we saw weeks ago, $Testify$ strictly dominates $Keep~Quiet$...so why would Guido mix between the two of them?
:::
---

## Getting Bad Probabilities {.smaller}
If you've solved for a player's mixed strategy and you find that the probability is 
**less than 0**, or **more than 1**:

::: {.incremental}
  * **It means something is wrong.** Probability can only be between 0 and 1 (inclusive).
  * Double-check your math---it could be an algebra error.
  * But if you're confident in your math, this means that there is **no way
  that the player would ever play a mixed strategy**: 
    + in fact, they have a strictly dominated strategy.
:::
---

## Mixed Strategies in the Deer Hunt

Consider the Deer Hunt:

| Igg, Ogg | Deer | Rabbit |
|----------+--------+----------|
| Deer     | $2, 2$ | $0, 1$   |
| Rabbit   | $1, 0$ | $1, 1$   |

Suppose that Igg hunts Deer 3/4 of the time, and Rabbit 1/4 of the time.

::: {.incremental}
  * If Ogg *always hunts deer*; 
  what is Ogg's *expected payoff*?
	* Ogg's expected payoff from playing Deer will be $0.75(2) + 0.25(0) = 1.5$.
:::
---

## Mixed Strategies in the Deer Hunt: Generalizing

We can generalize this approach to calculate Ogg's expected payoffs from any strategy that Igg chooses to play:

::: {.incremental}
  * Suppose Igg plays Deer with prob p, and Rabbit with prob 1 - p.
  * Ogg's expected payoff from Deer is:
    + $2(p) + 0(1 - p) = 2p$, 
  * and from Rabbit:
    +  $1(p) + 1(1 - p) = 1$.
  * Ogg's expected payoff from Deer gets larger with p:
    - more likely Igg is to hunt Deer, more attractive Deer becomes to Ogg.
:::
---

## MSNE in the Deer Hunt
We already saw that Ogg's expected payoffs from Deer and Rabbit are $2p$ and $1$, respectively, 

so Ogg would only play a mixed strategy if $p = \frac{1}{2}$.

::: {.incremental}
  * Likewise, Igg's expected payoffs are $2q$ and $1$, and Igg will play a mixed strategy if $q = \frac{1}{2}$.
  * The MSNE in this game can be written as:
  $\{(1/2~Deer, 1/2~Rabbit)_{Ogg}, \ (1/2~Deer, 1/2~Rabbit)_{Igg}\}$.
:::

---

## Error-Checking

Make sure that you're setting up the equations used to solve for a player's strategy correctly:

::: {.incremental}
  * Describe when a player is *indifferent* between their pure strategies: 
    + if you're trying to figure out when **Player 1** is indifferent, you need to use **Player 1's** payoffs.
  * However, the probabilities will be based on the **other** player's mixed strategy: 
    + in a game with mixed strategies, the randomness a player deals with is created by the **other** player---not themselves.
:::

---

## Another Example: Police Patrol and Drug Trade {.smaller}

| Police, Dealer | Streets (d) | Park (1 - d) |
|----------------+-------------+--------------|
| Streets (p)    | 80, 20      | 0,100        |
| Park (1 - p)   | 10, 90      | 60,40        |

^[Harrington, pg. 226]

::::: {.columns}
:::: {.column}
::: {.incremental}
  * Police Officer's expected utility:
    + $U_P(Streets) = 80d + 0(1-d)$
      - $= 80d$ 
    + $U_P(Park) = 10d + 60(1-d)$
      - $= 60 - 50d$.
:::
::::
:::: {.column}
::: {.incremental}
  * Drug Dealer's expected utility:
    + $U_D(Streets) = 20p + 90(1-p)$
      - $= 90 - 70p$ 
    + $U_D(Park) = 100p + 40(1-p)$
      - $= 40 + 60p$.
:::
::::
:::::
---

## MSNE in Patrol and Trade game:
* When is the Police Officer indifferent between Park and Streets?

* When is the Drug Dealer indifferent between Park and Streets?

  * What is the [Mixed Strategies Nash equilibrium?]{.hi}
---

## Graph Police Officer's expected utilities

```{r}
#| echo: false
# Load necessary libraries
library(ggplot2)

# Define the expected utility functions for Streets and Park
U_Streets <- function(d) {
  80 * d
}

U_Park <- function(d) {
  60 - 50 * d
}

# Generate a sequence of values for d from 0 to 1
d_values <- seq(0, 1, length.out = 100)

# Compute the expected utilities for each value of d
streets_utilities <- U_Streets(d_values)
park_utilities <- U_Park(d_values)

# Create a data frame for plotting
data <- data.frame(d = d_values, Streets = streets_utilities, Park = park_utilities)

# Plot the expected utilities and indicate the best response threshold
ggplot(data, aes(x = d)) +
  geom_line(aes(y = Streets, color = "Streets (80d)"), linewidth = 2) +
  geom_line(aes(y = Park, color = "Park (60 - 50d)"), linewidth = 2) +
  geom_vline(xintercept = 6/13, linetype = "dashed", color = "grey50") +
  annotate("text", x = 6/13, y = 0, label = "d = 6/13", hjust = -0.1, color = "grey50") +
  labs(title = "Expected Utility Functions for Streets and Park",
       x = "Probability (d)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```

---

## Graph Drug Dealer's expected utilities
 
```{r}
#| echo: false

# Define the updated expected utility functions for the Drug Dealer
U_Streets_D <- function(p) {
  90 - 70 * p
}

U_Park_D <- function(p) {
  40 + 60 * p
}

# Generate a sequence of values for p from 0 to 1
p_values <- seq(0, 1, length.out = 100)

# Compute the expected utilities for each value of p
streets_utilities_D <- U_Streets_D(p_values)
park_utilities_D <- U_Park_D(p_values)

# Create a data frame for plotting
data_D <- data.frame(p = p_values, Streets = streets_utilities_D, Park = park_utilities_D)

# Plot the expected utilities and indicate the best response threshold
ggplot(data_D, aes(x = p)) +
  geom_line(aes(y = Streets, color = "Streets (90 - 70p)"), linewidth = 2) +
  geom_line(aes(y = Park, color = "Park (40 + 60p)"), linewidth = 2) +
  geom_vline(xintercept = 5/13, linetype = "dashed", color = "grey50") +
  annotate("text", x = 5/13, y = 0, label = "p = 5/13", hjust = -0.1, color = "grey50") +
  labs(title = "Expected Utility Functions for Streets and Park (Drug Dealer)",
       x = "Probability (p)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```

---

## Graph Best Response functions
 
```{r}
#| code-fold: true
#| message: false
#| warning: false

library(tidyverse)
library(latex2exp)

data <- tibble(
  d = c(0, 6/13, 6/13, 1),
  PR = c(0, 0, 1, 1),
  p = c(1, 5/13, 5/13, 0),
  DR = c(0, 0, 1, 1),
)

# Plot the best response functions
ggplot(data) +
  geom_hline(yintercept = 5/13, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 6/13, linetype = "dashed", color = "grey50") +
  geom_step(aes(x = d, y = PR, color = "Police Officer's Best Response"), direction = "hv", linewidth = 2) +
  geom_step(aes(x = DR, y = p, color = "Drug Dealer's Best Response"), direction = "hv", linewidth = 2) +
  geom_point(data = tibble(d = 6/13, p = 5/13), aes(x=d, y=p, color = "MSNE"), size = 3) +
  annotate("text", y = 5/13, x = 0, label = TeX("$p^* = 5/13$"), hjust = -0.1, vjust = 2, color = "grey50") +
  annotate("text", x = 6/13, y = 0, label = TeX("$d^* = 6/13$"), hjust = -0.2, vjust = 1, color = "grey50") +
  labs(title = "Best Response Functions for Mixed Strategy Nash Equilibrium",
       x = "Drug Dealer's Probability (d)",
       y = "Police Officer's Probability (p)",
       color = "Best Response") +
  theme_minimal()
```
---

## MSNE in Patrol and Trade game:

* Note that the players' asymmetric preferences result in an interior solution.

* Notice that it isn't a 50:50, it is more likely that both meet in the Park 
  than it is likely that they both meet in the Streets