---
title: "Palacios-Huerta (2003) msne in penalty kicks"
---

| Kicker, Goalie  | $Dominant_g$ | $NonDominant_g$ |
|-----------------+--------------+-----------------|
| $Dominant_k$    | 58.30        | 94.97           |
| $NonDominant_k$ | 92.91        | 69.92           |

Let $p$ be the probability of the kicker choosing $Dominant_k$
and $q$ be the probability of the goalie choosing $Dominant_g$.

## The kicker will mix when:

$$
\begin{align}
58.3\cdot q + 94.97\cdot (1-q) & = 92.91\cdot q + 69.92\cdot (1-q) \\
\Rightarrow 25.05 & = 59.66 \cdot q \\
\Rightarrow q^* & = 0.42
\end{align}
$$

```{r}
#| echo: false
# Load necessary libraries
library(ggplot2)

# Define the expected utility functions for Streets and Park
U_Dominant <- function(q) {
  58.3*q + 94.97*(1-q)
}

U_NonDominant <- function(q) {
  92.91*q + 69.92*(1-q)
}

# Generate a sequence of values for d from 0 to 1
q_values <- seq(0, 1, length.out = 100)

# Compute the expected utilities for each value of d
dominant_utilities <- U_Dominant(q_values)
nondominant_utilities <- U_NonDominant(q_values)

# Create a data frame for plotting
data <- data.frame(q = q_values, Dominant = dominant_utilities, NonDominant = nondominant_utilities)

# Plot the expected utilities and indicate the best response threshold
ggplot(data, aes(x = q)) +
  geom_line(aes(y = Dominant, color = "Dominant"), linewidth = 2) +
  geom_line(aes(y = NonDominant, color = "NonDominant"), linewidth = 2) +
  geom_vline(xintercept = 0.4198, linetype = "dashed", color = "grey50") +
  annotate("text", x =  0.4198, y = 0, label = "q = 42%", hjust = -0.1, color = "grey50") +
  labs(title = "Expected Utility of Kicker",
       x = "Probability of goalie going NonDominant (q)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```

## The goalie will mix when:

$$
\begin{align}
41.7\cdot p + 7.09\cdot (1-p) & = 5.03\cdot p + 30.08\cdot (1-p) \\
59.66\cdot p & = 22.99 \\
p^* & = 0.39
\end{align}
$$

```{r}
#| echo: false

U_Dominant <- function(p) {
  41.7*p + 7.09*(1-p)
}

U_NonDominant <- function(p) {
  5.03*p + 30.08*(1-p)
}
# Generate a sequence of values for d from 0 to 1
p_values <- seq(0, 1, length.out = 100)

# Compute the expected utilities for each value of d
dominant_utilities <- U_Dominant(p_values)
nondominant_utilities <- U_NonDominant(p_values)

# Create a data frame for plotting
data <- data.frame(p = p_values, Dominant = dominant_utilities, NonDominant = nondominant_utilities)

# Plot the expected utilities and indicate the best response threshold
ggplot(data, aes(x = p)) +
  geom_line(aes(y = Dominant, color = "Dominant"), linewidth = 2) +
  geom_line(aes(y = NonDominant, color = "NonDominant"), linewidth = 2) +
  geom_vline(xintercept = 0.3853, linetype = "dashed", color = "grey50") +
  annotate("text", x = 0.3853, y = 0, label = "p = 39%", hjust = -0.1, color = "grey50") +
  labs(title = "Expected Utility of Goalie",
       x = "Probability of kicker going NonDominant (p)",
       y = "Expected Utility",
       color = "Choice") +
  theme_minimal()
```

## Mixed-Strategy Nash Equilibrium

If the kickers and goalies were playing mixed strategies consistent with a Nash equilibrium of the strategic form game above,
we would predict to see the kickers kicking with their dominant foot about 42% of the time
and goalies blocking to the kicker's non-dominant side about 39% of the time.
