\documentclass{article}

% load packages
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18} 
\usepackage{multirow,array} % for payoff matrix formatting
\usepackage{adjustbox}
% use exsheets to create different versions with \vary{}{}
\usepackage{exsheets}
\SetupExSheets{
  headings = block-wp,
  solution/print = true % set this to true to print key
}

% mark mc options as correct with custom \correct command
\newcommand{\ShowAnswers}{false}
\renewcommand{\ShowAnswers}{true} %comment this out if you do not want to show the answers
\newcommand{\correct}{%
    \expandafter\ifstrequal\expandafter{\ShowAnswers}{true}{\bfseries}{}%
}

% document formatting settings
\geometry{left=1.0in,right=1.0in,top=0.75in,bottom=1.0in}
\setlength{\parindent}{0pt} % turn off para indenting

% title and date for cover page
\title{
    \textbf{Econ 327: Game Theory} \\ 
    Midterm Exam
    }
\author{University of Oregon}
\date{October 29th, 2025}

% DOCUMENT BEGINS HERE
\begin{document}

\maketitle

% SET VERSION NUMBER HERE: 
\variant{1}

\begin{center}
  \Large{\textbf{Version \vary{1}{2}}}
\end{center}

\PrintSolutionsTF{
  \begin{center}
   \textbf{\large ANSWER KEY}
  \end{center}
}{
% instructions section
\begin{itemize}
  \item Complete \textit{all} questions and parts. 
  All questions will be graded.
  \item Carefully explain all your answers on short and long answer questions.

  An incorrect answer with clear explanation will earn partial credit,
  an incorrect answer with no work will get zero points.

  \item 
  If you do not understand what a question is asking for, 
  ask for clarification. 
\end{itemize}

\underline{Allowed Materials:}

\begin{itemize}
  \item A single 5" by 3" note card
  \item A non-programmable calculator
  \item Pencils, color pens, eraser, ruler/straight-edge etc.
\end{itemize}

\vspace{1.0in}

% space for student to write their name
\makebox[.6\textwidth]{Name\enspace\hrulefill}

\vspace{0.5in}

\begin{center}
  \fbox{\fbox{\parbox{5.5in}{\centering
    Answer the questions in the spaces provided on the
    question sheets. If you run out of room for an answer,
    continue on the back of the page or another sheet of paper.}}}
\end{center}
\newpage
}

%------------------------------------------------------------------------------%

\section*{Multiple Choice}

% \includequestions[random=10]{questions/mc}
\includequestions[IDs={3,5,6,7,8,10,11,12,13,14}]{questions/mc}

%------------------------------------------------------------------------------%
\newpage

\section*{Long Answer}

\includequestions{questions/sequential}

\newpage

\includequestions[IDs={tbl2}]{questions/bigtable}

\newpage

\includequestions[IDs={subgame}]{questions/changeorder}

\newpage

\includequestions[IDs={vlccs}]{questions/contstrats.tex}

%------------------------------------------------------------------------------%


\PrintSolutionsTF{}{
\vspace*{\fill}

\section*{Extra Credit}
Pick a bid of any number between 0 and 2 bonus points
which will be matched with another random student's bid.
Whoever has the \textbf{lowest} bid will be awarded their bonus points,
the other student will earn zero points.
A tie will result in no bonus points being given.

\vspace{.5cm}

\makebox[4cm]{\textbf{Your Bid:}\enspace\hrulefill}
}
%------------------------------------------------------------------------------%


\end{document}
