\documentclass[addpoints]{exam}

% \printanswers
\CorrectChoiceEmphasis{\color{red}\bfseries}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{multirow,array} % for payoff matrix formatting
\usepackage[colorlinks,pdfusetitle,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}

\definecolor{crimson}{RGB}{ 170, 4, 36 }
\definecolor{darkblue}{RGB}{ 4, 47, 170 }
\definecolor{brown}{RGB}{ 111, 71, 2 }
\definecolor{periwinkle}{RGB}{ 90, 177, 204 }
\definecolor{ducksgreen}{HTML}{007030}

\geometry{left=1.0in,right=1.0in,top=1.0in,bottom=1.0in}
\pagestyle{headandfoot}
\lhead{EC327 Game Theory}
\chead{Homework 1}
\rhead{Fall 2025}
\runningheadrule

\title{
    \textbf{Econ 327: Game Theory} \\ 
    Homework $\#1$
    }
\author{University of Oregon}
\date{Due: Oct. 3$^{rd}$}

% exam-type question formatting
\renewcommand{\thequestion}{\textbf{Question \arabic{question}}}
\bracketedpoints

\begin{document}

\maketitle

\begin{center}
  \gradetable[h][questions]
\end{center}

\vspace{0.5in}

\begin{center}
  \textbf{For homework assignments:}
\end{center}

\begin{itemize}

%  \item DO NOT write your name:
%  this assignment will be graded anonymously. 
%  If you want to, you can include your student ID instead.

  \item Complete \textit{all} questions and parts.

  % I will select one question at random to be graded
  % according to the rubric on Canvas.

  \item You will be graded on not only the content of your work
    but on how clearly you present your ideas.
    Make sure that your handwriting is legible.
    Please use extra pages if you run out of space 
    but make sure that all parts of a question 
    are in the correct order when you submit.

  \item You may choose to work with others,
  but everyone must submit to Canvas individually.

  Please include the names of everyone who you worked with 
  below your own name.
 
\end{itemize}

\vspace{1.0in}

\makebox[.6\textwidth]{Name\enspace\hrulefill}

\vspace{0.5in}

% \begin{center}
%   \fbox{\fbox{\parbox{5.5in}{\centering
%     Answer the questions in the spaces provided on the
%     question sheets. If you run out of room for an answer,
%     continue on the back of the page or another sheet of paper.}}}
% \end{center}

\begin{questions}

\newpage


%------------------------------------------------------------------

\question%[20]

Consider a (heavily) simplified version of the popular board game \textit{Catan}.
In this version, there are only five map tiles numbered one through five.
There are two players, Andy and Booth, and each has two settlements placed on a tile.
Andy's settlements are on tiles 1 and 2 and Booth's settlements are on tiles 3 and 4.
On a players' turn, they roll a single fairly weighted die and if it lands face up on a number which matches the tile of one of their settlements, they earn one sheep card.
However, if the die lands on a 6, then the player who rolled it can steal one sheep from their opponent.

Suppose that it is Andy's turn to roll the die.

\begin{parts}
\part[4] What is Andy's expected payoff (in sheep)?
\vspace{25mm}
\part[4] What is Booth's expected payoff?
\vspace{25mm}
\end{parts}

\begin{solution}
  \part
  Andy's expected payoff is $\frac{1}{3} (1) + \frac{1}{3} (0) + \frac{1}{6} (0) + \frac{1}{6} (1) = \frac{1}{2}$

  \part
  Booth's expected payoff is $\frac{1}{3} (0) + \frac{1}{3} (1) + \frac{1}{6} (0) + \frac{1}{3} (-1) = \frac{1}{6} $

\end{solution}

\question

Watch the clip from the British Game show Golden Balls.
\url{https://youtu.be/bOwh9_lAeLA}
The specific game is called Golden Balls and is played between the two contestents after they have collected a pool of prize money together in other challenges.

Respond to the following questions about the game and briefly justify each answer.

\begin{parts}
  \part[2] 
  Do the players take their actions \textit{sequentially} or \textit{simultaneously}?
  \vspace{10mm}

  \part[2]
  Is Golden Balls a \textit{zero-sum} or a \textit{constant-sum} game? 
  \vspace{10mm}

  \part[2]
  What relevant \textit{information} is available to the players when taking their actions?
  \vspace{10mm}

  \part[2]
  How important is the stage where the constestants are told to talk with each other?
  Can communication be strategic?
  \vspace{5mm}

\end{parts}

\newpage

\question%[20]

Read the 2022 Policito Opinion article, 
\textit{How Game Theory Explains Why We Have to Sanction Putin : Even If It’s Costly}.

\url{https://www.politico.com/news/magazine/2022/04/21/russia-sanctions-game-theory-00026566}

\begin{parts}

  \part[4]
  List the tools from game theory that we've learned about in class
  which the authors use to argue their point.
  \vspace{25mm}

  \part[2] 
  What assumptions do the authors make in their simplified `Repeated Sanctions Game'?
  \vspace{25mm}

  \part[2]
  Do you find the authors' arguments convincing? Why or why not?
  \vspace{25mm}

\end{parts}

\begin{solution}

The authors' main point is that if the US and allies even if sanctions on Russia were costly to enact for those nations,
they were still important to deter either Russia in the future or other nations from breaking international law.
If the game in their tree diagram is played only once, the subgame perfect Nash equilibrium has Player 1 choosing to transgress
because Player 2's only rational strategy is to choose Don't Punish in both of their decision nodes.
Once Player 1 has already made the transgresssion, the cost of that transgression is already felt by Player 2 
and Sanctions will just decrease their payoff more.

However, the authors argue that because this game is likely to be repeated in the future, 
(either against Putin again or another world leader),
the payoff of deterring future transgressions should mean that Nato countries should apply sanctions on Russia
even though they will be costly in the short term.

\begin{parts}

  \part
  Relevant tools/terms which we have discussed include backwards induction,
  common knowledge of rationality, perfect information, Pareto dominance/efficiency,
  game tree/extensive form, forward-looking, subgame perfect Nash Equilibrium/rollback equilibrium.
  A complete answer should relate at least on of these terms to the international sanctions placed on Russia.

  \part
  Some potential answers are: 
  rationality of Putin, 
  the relative rankings of the payoffs in the game (i.e., international community prefers Don't Punish after Putin Transgresses over Sanctioning),
  the potential future players care about future iterations of the game enough,
  etc.

  \part
  For example, consider what happens if the payoff to Player 2 of Don't Punish after a Transgression is 
  $ -c - f $ where $f$ is the cost in the future to other Players observing that Transgressions will go unpunished.
  If $f > s$, i.e., if the future cost of additional repeated Transgressions outweighs the cost of sanctions today,
  then the equilibrium of the game changes to { Transgress, (Sanction if Transgress, Don't Punish if Don't Transgress) } because now Player 2 it is rational for Player 2 to Sanction after a Transgression, 
  where it wasn't rational in the original one-shot game.

\end{parts}
\end{solution}
\end{questions}

\end{document}
