## Median-Voter Theorem

> "Apparently, a democracy is a place where numerous elections are held at great
cost without issues and with interchangeable candidates" -- Gore Vidal

Political candidates sometimes have platforms that are more alike than different.

  * How can we explain this with game theory?

## Political Platform Game

Assume there is a single spectrum to rank political candidates:

  * \[0,1\]: set of potential platforms which could be chosen along this scale

Also, assume only two parties:

  * D(emocratic) or R(epublican)

Candidates from either party set their platform $x_i$, where $i\in\{D,R\}$

  * Voters choose the candidate who'se platform is closest to their ideology

---

## Voter Preference Distribution

```{r}
library(ggplot2)
library(dplyr)

# Define candidate positions
x_D <- 0.2
x_R <- 0.4
midpoint <- (x_D + x_R) / 2

# Generate voter distribution (centered at 0.5)
set.seed(2025)
voters <- data.frame(ideology = rnorm(10000, mean = 0.5, sd = 0.15)) %>%
  filter(ideology >= 0, ideology <= 1) %>%
  mutate(
    preference = ifelse(abs(ideology - x_D) < abs(ideology - x_R), "D", "R")
  )

# Plot
ggplot(voters, aes(x = ideology)) +
  # Histogram colored by voter preference
  geom_histogram(aes(x = ideology, y = ..density..), bins = 50, color = "white", boundary = 0) +
  # Density overlay
  # geom_density(color = "black", linewidth = 1, alpha = 0.7) +
  # Candidate and midpoint markers
  geom_vline(xintercept = c(x_D, x_R, midpoint),
             linetype = c("solid", "solid", "dashed"),
             color = c("blue", "red", "black"),
             linewidth = c(1.2, 1.2, 0.8)) +
  # Labels for regions
  annotate("text", x = 0.15, y = 4, label = "Vote for D", 
           fontface = "italic", size = 5, color = "blue4") +
  annotate("text", x = 0.85, y = 4, label = "Vote for R", 
           fontface = "italic", size = 5, color = "red4") +
  # Axis and legend formatting
  scale_x_continuous(
    breaks = c(0, x_D, midpoint, x_R, 1),
    labels = c("0", expression(x[D]), 
               expression((x[D] + x[R]) / 2), 
               expression(x[R]), "1")
  ) +
  scale_fill_manual(values = c("D" = "skyblue3", "R" = "tomato3"),
                    name = "Preferred candidate",
                    labels = c("Democrat (D)", "Republican (R)")) +
  labs(
    # title = "The Determination of a Winner in the Campaign",
    x = NULL,
    y = "Density of voters"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "top",
    panel.grid.minor = element_blank()
  )
```

  * Not a Nash: Democrats set too low of a platform.

---

## Voter Preference Distribution

```{r}
library(ggplot2)
library(dplyr)

# Define candidate positions
x_D <- 0.4
x_R <- 0.7
midpoint <- (x_D + x_R) / 2

# Generate voter distribution (centered at 0.5)
set.seed(2025)
voters <- data.frame(ideology = rnorm(10000, mean = 0.5, sd = 0.15)) %>%
  filter(ideology >= 0, ideology <= 1) %>%
  mutate(
    preference = ifelse(abs(ideology - x_D) < abs(ideology - x_R), "D", "R")
  )

# Plot
ggplot(voters, aes(x = ideology)) +
  # Histogram colored by voter preference
  geom_histogram(aes(x = ideology, y = ..density..), bins = 50, color = "white", boundary = 0) +
  # Density overlay
  # geom_density(color = "black", linewidth = 1, alpha = 0.7) +
  # Candidate and midpoint markers
  geom_vline(xintercept = c(x_D, x_R, midpoint),
             linetype = c("solid", "solid", "dashed"),
             color = c("blue", "red", "black"),
             linewidth = c(1.2, 1.2, 0.8)) +
  # Labels for regions
  annotate("text", x = 0.15, y = 4, label = "Vote for D", 
           fontface = "italic", size = 5, color = "blue4") +
  annotate("text", x = 0.85, y = 4, label = "Vote for R", 
           fontface = "italic", size = 5, color = "red4") +
  # Axis and legend formatting
  scale_x_continuous(
    breaks = c(0, x_D, midpoint, x_R, 1),
    labels = c("0", expression(x[D]), 
               expression((x[D] + x[R]) / 2), 
               expression(x[R]), "1")
  ) +
  scale_fill_manual(values = c("D" = "skyblue3", "R" = "tomato3"),
                    name = "Preferred candidate",
                    labels = c("Democrat (D)", "Republican (R)")) +
  labs(
    # title = "The Determination of a Winner in the Campaign",
    x = NULL,
    y = "Density of voters"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "top",
    panel.grid.minor = element_blank()
  )
```

  * Not a Nash: Democrats could steal more median voters from Republicans

---

## Nash in Political Platform Game

```{r}
library(ggplot2)
library(dplyr)

# Define candidate positions
x_D <- 0.49
x_R <- 0.51
midpoint <- (x_D + x_R) / 2

# Generate voter distribution (centered at 0.5)
set.seed(2025)
voters <- data.frame(ideology = rnorm(10000, mean = 0.5, sd = 0.15)) %>%
  filter(ideology >= 0, ideology <= 1) %>%
  mutate(
    preference = ifelse(abs(ideology - x_D) < abs(ideology - x_R), "D", "R")
  )

# Plot
ggplot(voters, aes(x = ideology, fill = preference)) +
  # Histogram colored by voter preference
  geom_histogram(aes(x = ideology, y = ..density..), bins = 50, color = "white", boundary = 0) +
  # Density overlay
  # geom_density(color = "black", linewidth = 1, alpha = 0.7) +
  # Candidate and midpoint markers
  geom_vline(xintercept = c(x_D, x_R, midpoint),
             linetype = c("solid", "solid", "dashed"),
             color = c("blue", "red", "black"),
             linewidth = c(1.2, 1.2, 0.8)) +
  # Labels for regions
  annotate("text", x = 0.15, y = 4, label = "Vote for D", 
           fontface = "italic", size = 5, color = "blue4") +
  annotate("text", x = 0.85, y = 4, label = "Vote for R", 
           fontface = "italic", size = 5, color = "red4") +
  # Axis and legend formatting
  scale_x_continuous(
    breaks = c(0, x_D, midpoint, x_R, 1),
    labels = c("0", "", "", "", "1")
  ) +
  scale_fill_manual(values = c("D" = "skyblue3", "R" = "tomato3"),
                    name = "Preferred candidate",
                    labels = c("Democrat (D)", "Republican (R)")) +
  labs(
    # title = "The Determination of a Winner in the Campaign",
    x = NULL,
    y = "Density of voters"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold"),
    legend.position = "top",
    panel.grid.minor = element_blank()
  )
```